
---
title: "Imagining Moral Identity: An account of moral testimony"
subtitle: "The constitutive moral function of narrative testimony"
author: "Montaque Reynolds"
date: 2024-06-29T12
bibliography: ["/home/redapemusic35/data_storage/library.bib", "/home/redapemusic35/data_storage/my.bib"]
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      countIncrementalSlides: false
---

```{r xaringan-fit-screen, echo=FALSE}
xaringanExtra::use_fit_screen()
```

```{r, load_refs, include=FALSE, cache=FALSE}
library(RefManageR)
BibOptions(check.entries = FALSE,
           bib.style = "authoryear",
           cite.style = "alphabetic",
           style = "text",
           hyperlink = FALSE,
           dashed = FALSE)
myBib <- ReadBib("/home/redapemusic35/data_storage/library.bib", check = FALSE)
```

# Robert Hopkins *What is Wrong with Moral Testimony?*

One is either an optimist or a pessimist with regards to moral testimony. An optimist says that there is nothing wrong with basing one's moral beliefs on moral testimony while a pessimist says that there is.

Either moral testimony does not make moral knowledge available, or if it does make it available, it is unusable because we need to be able grasp for ourselves the moral reasons behind a moral view.

