---
title: "Imagining Moral Identity"
subtitle: "The constitutive moral function of narrative testimony"
author: "Montaque Reynolds"
date: 2024-06-29T12
draft: false
cascade:
  type: docs
sidebar:
  open: true
bibliography: ["/home/redapemusic35/data_storage/library.bib", "/home/redapemusic35/data_storage/my.bib"]
weight: 1
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      countIncrementalSlides: false
---

```{r xaringan-fit-screen, echo=FALSE}
xaringanExtra::use_fit_screen()
```

```{r, load_refs, include=FALSE, cache=FALSE}
library(RefManageR)
BibOptions(check.entries = FALSE,
           bib.style = "authoryear",
           cite.style = "alphabetic",
           style = "text",
           hyperlink = FALSE,
           dashed = FALSE)
myBib <- ReadBib("/home/redapemusic35/data_storage/library.bib", check = FALSE)
```

# What is wrong with moral testimony?

Testimony is a legitimate source of belief more generally, but moral testimony is not a legitimate source of moral belief more specifically.

---

# Julia Driver and the Asymmetry Problem

* Moral judgments are more serious than other kinds of judgments, for instance aesthetic ones.

---

### Two possible Reasons

* Either moral testimony does not confer moral knowledge (unavailable)
* or moral testimony does confer moral knowledge, but the knowledge gained does not enable you to fulfill some other obligation, therefore mk is unsusable.

Hopkins argues that mk is unusable because

One must adhere to the norm of grounding your decision in moral factors. E.g., "You would have to talk about the justice of the union’s demands, the cost to those it serves, and so forth." `r Cite(myBib, "hopk07a")`

---

# Moral Testimony, A literature review

Hills 2009:

> But I will begin by agreeing with the optimists: I will simply accept that you can acquire moral knowledge through testimony.

--

But

> I will argue that a centrally important concept in moral epistemology is not moral knowledge, but what I call “moral understanding,” and that the latter relates to testimony and to expertise quite differently from the former.

---

This is because

> it plays a vital role in good character and in morally worthy action.

--

For instance

> If Eleanor fails to use her moral understanding, she is not properly oriented and she cannot act well. To act well on the basis of moral beliefs, it is not sufficient that you have moral understanding; you need to use it to form your moral beliefs too, so that your belief that your action is right, for example, is explained by the reasons why it is right. `r Citep(myBib, "hill09", 122)`

---

Therefore since her moral knowledge is not grounded in the right way,

* She cannot act well since good action is grounded in right motivation.
* Right motivation means that you are acting for the reasons that make your action right.

---

However, Hills adds,

> Since doing the right thing is very important, you should trust moral testimony from trustworthy and reliable sources and defer to moral experts if you cannot gain moral understanding.

---

```{r, results='asis', echo=FALSE}
PrintBibliography(myBib)
```
