---
title: "Alternative Epistemologies"
subtitle: "Fiction and Fictional Identities"
author: "Montaque Reynolds"
date: 2024-06-29T12
draft: false
cascade:
  type: docs
sidebar:
  open: true
bibliography: ["/home/redapemusic35/data_storage/library.bib"]
weight: 1
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      countIncrementalSlides: false
---

```{r xaringan-fit-screen, echo=FALSE}
xaringanExtra::use_fit_screen()
```

```{r, load_refs, include=FALSE, cache=FALSE}
library(RefManageR)
BibOptions(check.entries = FALSE,
           bib.style = "authoryear",
           cite.style = "alphabetic",
           style = "text",
           hyperlink = FALSE,
           dashed = FALSE)
myBib <- ReadBib("/home/redapemusic35/data_storage/library.bib", check = FALSE)
```

1. Modern conceptions of personhood are situated inside of social identities.
2. It is not clear that these equitably entail human agency.
3. Therefore sources of social identity is an underexplored topic in critical theory.

---

Epistemic Ecologies
* rich set of resources for characterizing epistemic communities and the embodiment of social knowledge
* socio-political imaginaries are embodied and affectively rich knowledge systems in epistemic communities (Dillion 2013)
* This knowledge informs the unspoken, commonly held 'affectively understood' sociopolitical imaginary, racial, gendered, and sexualized presumptions

???

According to Kate McLean and Mohammed Syed, there are three kinds of narratives that contribute to a narrative account of personhood.

---

### Some Brief Notes on Literary Narratives


* Any adequate theory of fiction must accommodate pictorial, as well as literary ones.
 `r Citep(myBib, "walt90", 75)` [@walt90, 75]
* Literary narratives, those "devised by single authors who were the creators of that literature" can "come[s] in many forms, from the highly self-conscious artistry of Aeschylean tragedy to the communally produced narratives of folklore" [@stum10, 29]
 * The Platonic dialogues, like works of tragic theater, but unlike many extant paradigms of ethical discourse . . . contain more than a single voice. [@nuss01i, 126]
* This, in turn, suggests that in order to talk well about them we will need to run to texts that contain a narrative dimension, thus deepening and refining our grasp of ourselves as beings with a complicated temporal history. [@nuss01i, 3]

---

However . . .


* Am I affectionate? Why?
* Am I Caring? Why?
* Am I Passionate? Why?

---

## Two Initial Approaches

Questions about who we are

* $\rightarrow$ where we fit in a larger social context
* $\rightarrow$ directions of our desires and longings in regard to interpersonal community
* $\rightarrow$ what are my personal feelings to those I live in society with

---

> Master narratives have been largely defined as culturally shared stories that guide thoughts, beliefs, values, and behaviors

But there are also

* Personal narratives
* alternative narratives

???

Those that are autobiographical (what Maria Schectman calls cultural), those that are biographical (self), and those that are under-explored, what I call literary. I consider the possible contributions of literary narratives to the autobiographical and biographical [@sche24].

Biographical narratives are social. An early concern with conceptualizing identity development in persons, was understanding the contribution one's social environment made towards developing her personality. Narrative has offered a way for us to understand this relationship.

---


